---
title: "Challenge3"
author: "Danny Cam Hoa Tien"
date: "2023-05-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##



```{r}
library (h2o)

library(tidyverse)

library(readxl)

library(skimr)

library(GGally)

```

##

You can also embed plots, for example:

```{r}
h2o.init()

```

```{r}
hp_by_cyl <- mtcars %>% 
  group_by(cyl) %>%
  summarize(min_hp=min(hp),
            max_hp=max(hp))
hp_by_cyl

```

```{r}

groupby_var <- quo(vs)

hp_by_vs <- mtcars %>% 
              group_by(!!groupby_var) %>%
              summarize(min_hp=min(hp),
                        max_hp=max(hp))
hp_by_vs

```

```{r}
car_stats <- function(groupby_var, measure_var) {

    groupby_var <- enquo(groupby_var)
    measure_var <- enquo(measure_var)
    
    ret <- mtcars %>% 
      
             group_by(!!groupby_var) %>%
             summarize(min = min(!!measure_var), max = max(!!measure_var)) %>%
      
             # Optional: as_label() and "walrus operator" :=
             mutate(
               measure_var = as_label(measure_var), !!measure_var := "test"
               )
    
    return(ret)

}
car_stats(am,hp)

car_stats(gear,cyl)

```

```{r}

scatter_plot <- function(data, x_var, y_var) {
  
  x_var <- enquo(x_var)
  y_var <- enquo(y_var)
  
  ret <- data %>% 
           ggplot(aes(x = !!x_var, y = !!y_var)) + 
           geom_point() + 
           geom_smooth() +
           ggtitle(str_c(as_label(y_var), " vs. ",as_label(x_var)))
 
  return(ret)
}
scatter_plot(mtcars, disp, hp)

```
#Business Case

```{r}

employee_attrition_tbl <- read_csv("datasets-1067-1925-WA_Fn-UseC_-HR-Employee-Attrition.csv")


```
# Business & Data Understanding: Department and Job Role

```{r}


# Data subset
dept_job_role_tbl <- employee_attrition_tbl %>%
  select(EmployeeNumber, Department, JobRole, PerformanceRating, Attrition)

dept_job_role_tbl %>%

  group_by(Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%
  mutate(pct = n / sum(n))

```
# Attrition by department
```{r}
dept_job_role_tbl %>%

  # Block 1
  group_by(Department, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%

  # Block 2: Caution: It's easy to inadvertently miss grouping when creating counts & percents within groups
  group_by(Department) %>%
  mutate(pct = n / sum(n))

```
# Attrition by job role
```{r}

dept_job_role_tbl %>%

  # Block 1
  group_by(Department, JobRole, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%

  # Block 2
  group_by(Department, JobRole) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup() %>%

  # Block 3
  filter(Attrition %in% "Yes")

```
# Develop KPI
```{r}

dept_job_role_tbl %>%

  # Block 1
  group_by(Department, JobRole, Attrition) %>%
  summarize(n = n()) %>%
  ungroup() %>%

  # Block 2
  group_by(Department, JobRole) %>%
  mutate(pct = n / sum(n)) %>%
  ungroup() %>%

  # Block 3
  filter(Attrition %in% "Yes") %>%
  arrange(desc(pct)) %>%
  mutate(
    above_industry_avg = case_when(
      pct > 0.088 ~ "Yes",
      TRUE ~ "No"
    )
  )

```

```{r}
# Function to calculate attrition cost
calculate_attrition_cost <- function(

  # Employee
  n                    = 1,
  salary               = 80000,

  # Direct Costs
  separation_cost      = 500,
  vacancy_cost         = 10000,
  acquisition_cost     = 4900,
  placement_cost       = 3500,

  # Productivity Costs
  net_revenue_per_employee = 250000,
  workdays_per_year        = 240,
  workdays_position_open   = 40,
  workdays_onboarding      = 60,
  onboarding_efficiency    = 0.50

) {

  # Direct Costs
  direct_cost <- sum(separation_cost, vacancy_cost, acquisition_cost, placement_cost)

  # Lost Productivity Costs
  productivity_cost <- net_revenue_per_employee / workdays_per_year *
    (workdays_position_open + workdays_onboarding * onboarding_efficiency)

  # Savings of Salary & Benefits (Cost Reduction)
  salary_benefit_reduction <- salary / workdays_per_year * workdays_position_open

  # Estimated Turnover Per Employee
  cost_per_employee <- direct_cost + productivity_cost - salary_benefit_reduction

  # Total Cost of Employee Turnover
  total_cost <- n * cost_per_employee

  return(total_cost)

}

calculate_attrition_cost()
## [1] 78483.33
calculate_attrition_cost(200)
## [1] 15696667

```
# Function to convert counts to percentages. 


#Function For Block 3



```{r}

source("C:/Users/tiend/Documents/GitHub/ss23-bdml-tiend96/Challenge3/assess_atrition.R")
source("C:/Users/tiend/Documents/GitHub/ss23-bdml-tiend96/Challenge3/count_to_pct.R")

dept_job_role_tbl %>%

  count(Department, JobRole, Attrition) %>%
  count_to_pct(Department, JobRole) %>%
  assess_attrition(Attrition, attrition_value = "Yes", baseline_pct = 0.088) %>%
  mutate(
    cost_of_attrition = calculate_attrition_cost(n = n, salary = 80000)
  )

```






```{r}

# This will return a quoted result
colnames(dept_job_role_tbl)[[1]]
## "EmployeeNumber"

# This will become an unquoted expression
rlang::sym(colnames(dept_job_role_tbl)[[1]])
## EmployeeNumber

# quos() captures it and turns it into a quosure, which is a list
# Will be evaluated at the time we use the double !! later on in the code.
# Then it will turn it into EmployeeNumber
quos(rlang::sym(colnames(employee_attrition_tbl)[[1]]))
## <list_of<quosure>>
##
## [[1]]
## <quosure>
## expr: ^rlang::sym(colnames(employee_attrition_tbl)[[1]])
## env:  global

# If the user supplies two different columns such as Department and Job Role
# or if the user does not supply a column the length will be different
quos(Department, JobRole) 
quos(Department, JobRole) %>% length()
## 2
quos() %>% length
## 0

```

```{r}

source("C:/Users/tiend/Documents/GitHub/ss23-bdml-tiend96/Challenge3/plot_attrition.R")


dept_job_role_tbl %>%

  # Select columnns
  count(Department, JobRole, Attrition) %>%
  count_to_pct(Department, JobRole) %>%
  
  assess_attrition(Attrition, attrition_value = "Yes", baseline_pct = 0.088) %>%
  mutate(
    cost_of_attrition = calculate_attrition_cost(n = n, salary = 80000)
  ) %>%

  # Select columnns
  plot_attrition(Department, JobRole, .value = cost_of_attrition,
                 units = "M") +
  labs(
    title = "Estimated Cost of Attrition by Job Role",
    x = "Cost of Attrition",
    subtitle = "Looks like Sales Executive and Labaratory Technician are the biggest drivers of cost"
  )

```
## 2. Data Understanding

# Load Data data definitions
```{r}

path_data_definitions <- "C:/Users/tiend/Documents/GitHub/ss23-bdml-tiend96/Challenge3/data_definitions.xlsx"
definitions_raw_tbl   <- read_excel(path_data_definitions, sheet = 1, col_names = FALSE)

employee_attrition_tbl


```

```{r}

# Descriptive Features
employee_attrition_tbl %>% select(Age, DistanceFromHome, Gender, MaritalStatus, NumCompaniesWorked, Over18)

# Employment Features
employee_attrition_tbl %>% select(Department, EmployeeCount, EmployeeNumber, JobInvolvement, JobLevel, JobRole, JobSatisfaction)

# Compensation Features
employee_attrition_tbl %>% select(DailyRate, HourlyRate, MonthlyIncome, MonthlyRate, PercentSalaryHike, StockOptionLevel)

# Survery Results
employee_attrition_tbl %>% select(EnvironmentSatisfaction, JobSatisfaction, RelationshipSatisfaction, WorkLifeBalance)

# Performance Data
employee_attrition_tbl %>% select(JobInvolvement, PerformanceRating)

# Work-Life Features
employee_attrition_tbl %>% select(BusinessTravel, OverTime)

# Training & Education
employee_attrition_tbl %>% select(Education, EducationField, TrainingTimesLastYear)

# Time-Based Features
employee_attrition_tbl %>% select(TotalWorkingYears, YearsAtCompany, YearsInCurrentRole, YearsSinceLastPromotion, YearsWithCurrManager)

```

```{r}

# Step 1: Data Summarization -----

skim(employee_attrition_tbl)

# Character Data Type
employee_attrition_tbl %>%
    select_if(is.character) %>%
    glimpse()

# Get "levels"
employee_attrition_tbl %>%
    select_if(is.character) %>%
    map(unique)

# Proportions    
employee_attrition_tbl %>%
    select_if(is.character) %>%
    map(~ table(.) %>% prop.table())

# Numeric Data
employee_attrition_tbl %>%
    select_if(is.numeric) %>%
    map(~ unique(.) %>% length())

employee_attrition_tbl %>%
    select_if(is.numeric) %>%
    map_df(~ unique(.) %>% length()) %>%
    # Select all columns
    pivot_longer(everything()) %>%
    arrange(value) %>%
    filter(value <= 10)

```
# Step 2: Data Visualization ----
```{r}



employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    ggpairs() 

```

```{r}

employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    ggpairs(aes(color = Attrition), lower = "blank", legend = 1,
            diag  = list(continuous = wrap("densityDiag", alpha = 0.5))) +
    theme(legend.position = "bottom")

```
# Create data tibble, to potentially debug the plot_ggpairs function (because it has a data argument)
```{r}

data <- employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome)

plot_ggpairs <- function(data, color = NULL, density_alpha = 0.5) {
    
    color_expr <- enquo(color)
    
    if (rlang::quo_is_null(color_expr)) {
        
        g <- data %>%
            ggpairs(lower = "blank") 
        
    } else {
        
        color_name <- quo_name(color_expr)
        
        g <- data %>%
            ggpairs(mapping = aes_string(color = color_name), 
                    lower = "blank", legend = 1,
                    diag = list(continuous = wrap("densityDiag", 
                                                  alpha = density_alpha))) +
            theme(legend.position = "bottom")
    }
    
    return(g)
    
}

employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    plot_ggpairs(color = Attrition)

```

```{r}

# Explore Features by Category

#   1. Descriptive features: age, gender, marital status 
employee_attrition_tbl %>%
    select(Attrition, Age, Gender, MaritalStatus, NumCompaniesWorked, Over18, DistanceFromHome) %>%
    plot_ggpairs(Attrition)

#   2. Employment features: department, job role, job level
employee_attrition_tbl %>%
    select(Attrition, contains("employee"), contains("department"), contains("job")) %>%
    plot_ggpairs(Attrition) 

#   3. Compensation features: HourlyRate, MonthlyIncome, StockOptionLevel 
employee_attrition_tbl %>%
    select(Attrition, contains("income"), contains("rate"), contains("salary"), contains("stock")) %>%
    plot_ggpairs(Attrition)

#   4. Survey Results: Satisfaction level, WorkLifeBalance 
employee_attrition_tbl %>%
    select(Attrition, contains("satisfaction"), contains("life")) %>%
    plot_ggpairs(Attrition)

#   5. Performance Data: Job Involvment, Performance Rating
employee_attrition_tbl %>%
    select(Attrition, contains("performance"), contains("involvement")) %>%
    plot_ggpairs(Attrition)

#   6. Work-Life Features 
employee_attrition_tbl %>%
    select(Attrition, contains("overtime"), contains("travel")) %>%
    plot_ggpairs(Attrition)

#   7. Training and Education 
employee_attrition_tbl %>%
    select(Attrition, contains("training"), contains("education")) %>%
    plot_ggpairs(Attrition)

#   8. Time-Based Features: Years at company, years in current role
employee_attrition_tbl %>%
    select(Attrition, contains("years")) %>%
    plot_ggpairs(Attrition)

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```

```{r}

```


